Data Preparation

### 2019-01-11 Data Preparation.Rmd
Course Data text

## Setup
Before importing the spreadsheets from the drive, let us create two vectors `list_assessment` and `list_AoD` which respectively list the `19` types of assessment and the `18` aims of the degree (AoD) of the degree which we take into consideration in the analysis. The information comes from a spreadsheet from our google drive *DARS* which we save as `lists`. In addition, we also create two additional vectors `list_assessment_plot` and `list_AoD_plot` which contain a selection of prominent assessment types and AoD that we will consider when ploting the data[^1].
```{r import list}
lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
lists <- list(
  Assessment      = lists_brut$Assessment,
  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
  )
rm(lists_brut)
```

@@

# Variable Engineering
##Course Data
### AoD
In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it, or if one of its assessments cover it. For instance, if one of ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.

@@

In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO <- d_ILO %>%
  select(Code, AoD) %>%
  unique
print(d_AoD_ILO)
```

@@

In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers. We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`. `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`.

@@

Similarly to what we did with the tibble `d_AoD_ILO`, we first eliminate the AoD that are not covered by the assessments and then we take the unique combination of course and AoD in case a course had several assessments covering the same AoD.
```{r d_AoD_assessment distinct}
d_AoD_assessment <- d_AoD_assessment %>%
  select(Code, AoD) %>%
  distinct
print(d_AoD_assessment)
```

#### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
```{r rbind d_AoD_ILO and d_AoD_assessment}
d_AoD <- rbind(d_AoD_ILO,
               d_AoD_assessment) %>%
  distinct %>%
  arrange(Code)
rm(d_AoD_ILO, d_AoD_assessment)
print(d_AoD)
```

@@

d_description <- stem_with_dictionary(d_description)
d_overview <- stem_with_dictionary(d_overview)
d_manual <- stem_with_dictionary(d_manual)
rm(stems, stem_hunspell, stem_with_dictionary)
print(d_overview) # See humanities - humanity
```
### Removing Stopwords
```{r}
# Own stop words
sw_own <- c("______________________________________________________________________________")
remove_sw <- function(data) data %>%
  filter(! word %in% c(stop_words$word, sw_own))
d_description <- remove_sw(d_description)
d_overview <- remove_sw(d_overview)
d_manual <- remove_sw(d_manual)
rm(sw_own, remove_sw)
```

>>>>

## Setup
First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`. ` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively). We also any imported emtpy cells.
```{r import list}
lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
lists <- list(
  Assessment      = lists_brut$Assessment,
  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
  )
rm(lists_brut)
```

@@

# Variable Engineering
##Course Data
The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.

### AoD
In this analysis, we conside that a course can cover an AoD in two ways: a course covers an AoD if one of its ILOs covers it, or if one of its assessments cover it. For instance, if one of ILO of a course states that the students will learn to analyze empirical data in the context of academic research, then the course in question covers the AoD `Research Skills`; and if one of the assessment is a group presentation, then the course also covers the AoD `Collaborative Skills` and `Communication Skills`.

@@

In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO <- d_ILO %>%
  select(Code, AoD) %>%
  distinct
print(d_AoD_ILO)
```

@@

In order to determine which AoD each course covers with its assessments, we need to create a binary matrix which indicates which AoD(s) each assessment type covers. We have created such matrix on our google drive and we save it in the following piece of code as `map_assessment_AoD`. `map_assessment_AoD` indicates that, for instance, the assessment type `Essay` covers the AoD `Critical Thinking Skills`, `Communication Skills` and `Writing Skill`. Thus, the first step is to import this matrix:

@@

Next, we keep ony one copy of each distinct combination of course and AoD in case a course had several assessments covering the same AoD (this is analogous to what we did with the tibble `d_AoD_ILO`).
```{r d_AoD_assessment distinct}
d_AoD_assessment <- d_AoD_assessment %>%
  select(Code, AoD) %>%
  distinct
print(d_AoD_assessment)
```

#### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
```{r rbind d_AoD_ILO and d_AoD_assessment}
d_AoD <- rbind(d_AoD_ILO,
               d_AoD_assessment) %>%
  distinct %>%
  arrange(Code)
rm(d_AoD_ILO, d_AoD_assessment)
print(d_AoD)
```

@@

d_description <- stem_with_dictionary(d_description)
d_overview <- stem_with_dictionary(d_overview)
d_manual <- stem_with_dictionary(d_manual)
rm(stems, stem_hunspell, stem_with_dictionary)
print(d_overview) # See humanities - humanity
```
### Removing Stopwords

```{r}
# Own stop words
sw_own <- c("______________________________________________________________________________")
remove_sw <- function(data) data %>%
  filter(! word %in% c(stop_words$word, sw_own))
d_description <- remove_sw(d_description)
d_overview <- remove_sw(d_overview)
d_manual <- remove_sw(d_manual)
rm(sw_own, remove_sw)
```
